%% eKL_v01.tex
%% V1.0
%% 2009/09/01
%% by Norsyidah Mat Saat @ Abas
%% for requirement of Client Server Computing class
%%
%% This is a review paper on eKL

\documentclass[conference, compsoc]{IEEEtran}
% Add the compsoc option for Computer Society conferences.

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{eKL - Its Implementation and Issues}


% author names and affiliations

\author{\IEEEauthorblockN{Norsyidah binti Mat Saat @ Abas}
\IEEEauthorblockA{Faculty of Technology and Information Sciences  \\
National University of Malaysia (UKM)\\
Bangi, Selangor, Malaysia \\
Email: aznor98@yahoo.com }
}

% make the title area
\maketitle


\begin{abstract}
%\boldmath
eKL is an ICT initiatives in public sector. It is developed by MAMPU, Prime Minister's Department (JPM).   

\end{abstract}


\section{Introduction}
% no \IEEEPARstart
eKL is an initiative to improve the service delivery system of Government agencies in Klang
Valley. The rationale behind the establishment of eKL is: to accelerate the achievement of excellence in service delivery for agencies within the Klang Valley, to push the implementation of Electronic Government in the Klang Valley for more efficient, fast, quality, safe and people friendly services that will have an impact on the public, to ensure that by 2010, the implementation of the electronic government in the Klang Valley be used as an example for the implementation to the rest of the country and to support the Broadband Push program.

% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)


\subsection{Vision of eKL}
Th eKL vision statement is: "Delivering services through an integrated and connected Klang Valley".

\subsection{Mission of eKL}
To strenghten/enhance the Government service delivery system within Klang Valley, through the use of ICT, to deliver efficient, fast, quality, safe and people friendly services that will have an impact on the public.

\subsection{Objective of eKL}
(a) One Government Many Agencies
(b) No Wrong Door
(c) End to End interactive online services (24x365) 
(d) Sharing of services and information
(e) Raising Competitive Edge

\subsection{eKL Coverage}
(a) Selangor : Shah Alam, Petaling Jaya, Daerah Petaling, Klang, Gombak, Hulu Langat, Kuala Langat, Kuala Selangor,Sepang (KLIA and Cyberjaya,  

(b) Wilayah Persekutuan Kuala Lumpur and Putrajaya,

(c) Negeri Sembilan : Nilai

It involves 3 cities : KL, PJ and Shah Alam with a total Population of 6.4 million people. 


\section{eKL Framework}


\section{Conclusion}
The conclusion goes here. this is more of the conclusion

% conference papers do not normally have an appendix


% use section* for acknowledgement
\section*{Acknowledgment}


The author would like to thank Client Server Computing class's instructor, Mr. Mohd. Zamri Murah for his guidance and passion in sharing with his students the knowledge. Also to coursemates: Razale, Mohd. Asri, Hadi Jehmica Abdullah, Doli Anggia Harahap, and others. 


% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\bibitem
Dr. Lili Nurliyana Abdullah, \emph{ICT: The Agent of Transformation in Service Delivery}, Public Sector ICT Management Review, July - December 2008 Vol.2 No. 2\relax, page 5-9

\bibitem
http://www.ekl.gov.my/content/view/382/135/


\end{thebibliography}




% that's all folks
\end{document}


